---
title: "Reproducible Research-Course Project 1"
output: html_document
---

```{r setup, include=TRUE, echo=TRUE}
library(ggplot2)
library(dplyr)
```


```{r, include=TRUE, echo=TRUE} 
        #1.What is mean total number of steps taken per day?
        #1. Code for reading in the dataset and/or processing the data
        getwd()
        activity<- read.csv("activity.csv")
        perday<-aggregate(activity$steps, by=list(activity$date), FUN=sum)
        summary(perday)

        #2. Histogram of the total number of steps taken each day
        ggplot(perday, aes(x=x)) + geom_histogram(color="black", fill="light blue", bins=5) +xlab("Steps per Day") + ylab("Frequency")

        #3. Mean and median number of steps taken each day
        median<- median(activity$steps, na.rm=T)
        mean<-mean(activity$steps, na.rm=T)
        values<-rbind(median,mean)
        print(values)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r,include=TRUE, echo=TRUE}
#2.What is the average daily activity pattern?

        #1. Time series plot of the average number of steps taken
        activity2<-perday<-aggregate(activity$steps, by=list(activity$interval), FUN=mean, na.rm=T)

        #2.The 5-minute interval that, on average, contains the maximum number of steps
        plot(x~Group.1, data=activity2, type="l", xlab="Interval", ylab="Average Steps")

```

```{r,include=TRUE, echo=TRUE}
#3.Imputing missing values
        #1. Code to describe and show a strategy for imputing missing data
        sum(is.na(activity$steps))

        #2,3,4. Histogram of the total number of steps taken each day after missing values are imputed
        new_data<-aggregate(activity$steps, by=list(activity$date), FUN=sum)
        ggplot(new_data, aes(x=x)) + geom_histogram(color="black", fill="light blue", bins=5) +xlab("Steps per Day") + ylab("Frequency")
        median2<- median(new_data$x, na.rm=T)
        mean2<-mean(new_data$x,na.rm=T)
        values2<-rbind(median2,mean2)
        print(values2)

```

```{r,include=TRUE, echo=TRUE}
#4.Are there differences in activity patterns between weekdays and weekends?
        #1.Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating            whether a given date is a weekday or weekend
        library(lubridate)
        activity$days<-wday(as.Date(activity$date,'%Y-%m-%d'), label=T)
        weekends<- subset(activity, activity$days == "Sat"| activity$days=="Sun", na.rm=T)
        weekends<-aggregate(weekends$steps, by=list(weekends$interval), FUN=mean, na.rm=T)
        weekdays<-subset(activity, activity$days !="Sat" & activity$days!="Sun", na.rm=T)
        weekdays<-aggregate(weekdays$steps, by=list(weekdays$interval), FUN=mean, na.rm=T)

        #2. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and         weekends
        par(mfrow=c(2,1),mar=c(4,4,2,1))
        plot(x~Group.1, data=weekends, type="l", xlab="Interval", ylab="Average Steps", main="Weekdays")
        plot(x~Group.1, data=weekdays, type="l", xlab="Interval", ylab="Average Steps", main="Weekends")





